```
Title: "Assessment task 3.Rmd Report"
Author: "Aadi Sharma"
Student ID – “220167207”
Unit code: “SLE712”
Submission Date – “12.06.20”
Output type: html_document
Theme: cosmo
Source: 
```
## Part 1, Question 1. Downloading the file named “gene_expression.tsv” in to R, making the row names and showing a table of values for the first six genes
Here, we are using the download.file() command to import the file from github into R to solve the first 5 questions of the Part 1 assessment. To read into R properly, we have formatted the imported data by setting 'header = TRUE', 'stringsAsFactors = FALSE', and 'row.names = 1'.
```{r,chunk1, echo=TRUE}
# a link of the required datafile is downloaded from GitHub
download.file("https://raw.githubusercontent.com/markziemann/SLE712_files/master/bioinfo_asst3_part1_files/gene_expression.tsv", destfile = "gene_expression.tsv")
# reading the data frame in to RStudio
# recognising the header 
# using the first column as the rownames
# avoiding strings to be recognised as Factors
x <-read.table("gene_expression.tsv", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
``` 
### Checking the data integrity
In this section, we are using head()command to read first six lines of the data frame and using str() to make sure that data is recognised as numeric.

```{r, chunk2, echo=TRUE}
# checking the first six lines of the data frame
head(x)
# checking the structure of the data to confirm the presence of numerical and integers data structure
str(x)
```
## Question 2. Making a new column as mean of the other columns and showing a table of values for the first six genes. 
In this part, we are using subset command to make a new column which will be mean of the other columns.

```{r, chunk3, echo=TRUE}
# x is the dataframe
# new column is named 'mean2' to calculate the mean
x$mean2 <- rowMeans(x)
# checking the first six lines of the data
head(x)
```


