```
Title: "Assessment task 3.Rmd Report"
Author: "Aadi Sharma"
Student ID – "220167207"   
Unit code: "SLE712"
Submission Date – "12.06.20"   
Output type: html_document
Theme: cosmo
Source: https://github.com/sharmaaad/Final-Assignment-3-SLE712.git 
```
## Part 1, Question 1. Downloading the file named “gene_expression.tsv” in to R, making the row names and showing a table of values for the first six genes
Here, we are using the download.file() command to import the file from github into R to solve the first 5 questions of the Part 1 assessment. To read into R properly, we have formatted the imported data by setting 'header = TRUE', 'stringsAsFactors = FALSE', and 'row.names = 1'.
```{r,chunk1, echo=TRUE}
# a link of the required datafile is downloaded from GitHub
download.file("https://raw.githubusercontent.com/markziemann/SLE712_files/master/bioinfo_asst3_part1_files/gene_expression.tsv", destfile = "gene_expression.tsv")
# reading the data frame in to RStudio
# recognising the header 
# using the first column as the rownames
# avoiding strings to be recognised as Factors
x <-read.table("gene_expression.tsv", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
``` 
### Checking the data integrity
In this section, we are using head()command to read first six lines of the data frame and using str() to make sure that data is recognised as numeric.

```{r, chunk2, echo=TRUE}
# checking the first six lines of the data frame
head(x)
# checking the structure of the data to confirm the presence of numerical and integers data structure
str(x)
```
## Question 2. Making a new column as mean of the other columns and showing a table of values for the first six genes. 
In this part, we are using subset command to make a new column which will be mean of the other columns.

```{r, chunk3, echo=TRUE}
# x is the dataframe
# new column is named 'mean2' to calculate the mean
x$mean2 <- rowMeans(x)
# checking the first six lines of the data
head(x)
```
## Question 3.  Listing the 10 genes with the highest mean expression 
In order to find 10 genes with the highest mean expression, we command the re-ordering of the column named 'mean2'.

```{r, chunk4, echo=TRUE}
# initially, order the column named 'mean2'
order(x$mean2)
# then, by using square brackets, we re-order the column
x[order(-x$mean2),]
x_sorted <- x[order(-x$mean2),]
# in the end, by using head() command figured out 10 genes with the highest mean expression
head(x_sorted,10)
```
## Question 4. Determining the number of genes with a mean <10 
In this section, we are filtering the column named 'mean2' to calculate a mean <10. 
```{r, chunk5, echo=TRUE}
# using filter function
filtered <- subset(x, mean2 > 10)
# filtering the number of rows
nrow(filtered)
```
## Question 5. Making a histogram plot of the mean values in png format
In this segment, we use the hist() function to make a histogram plot of the mean values of the column named 'mean2' of the provided data.
```{r, chunk6, echo=TRUE}
# using the hist() command on the column named 'mean2' of the data 'x'
hist(x$mean2)
# to distribute the data frame properly, dividing it by breaks of 30
hist(x$mean2,breaks=30)
```
## Question 6. Importing the cvs file named “growth_data.csv” into an R object to find out the column names
Here, we are using the download.file() command to download the file from github into R to solve the last 5 questions of Part 1 of the assessment. To read into R properly with read.csv() command, we have formatted the imported data by setting 'header = TRUE', 'stringsAsFactors = FALSE', and 'row.names = 1'.

```{r, chunk7, echo=TRUE}
# a link of another data frame is downloaded from GitHub
download.file("https://raw.githubusercontent.com/markziemann/SLE712_files/master/bioinfo_asst3_part1_files/growth_data.csv", destfile = "growth_data.csv")
# in order to import "comma separated" values of the data file correctly, we use read.csv() command
y<-read.csv("growth_data.csv")
# reading the data frame into R
# recognising the header
# avoiding strings to be recognised as Factors
y <-read.csv("growth_data.csv", header = TRUE, stringsAsFactors = FALSE)
```
### Checking the data integrity
In this section, we are using str() command to make sure that data is recognised as numeric and we are also naming the columns by using the subset function. 

```{r, chunk8, echo=TRUE}
# checking the structure of the data to confirm that it has numerical and integers
str(y)
# to name the columns we can use the subset()command as the data values are 'characters'
subset(y,Site=="northeast")
colnames(y)
````
## Question 7. Calculating the mean and standard deviation of tree circumference at the start and end of the study at both sites
Here, we are using subset() command to find out the mean and standard deviation of tree circumference of two different sites which are 'northeast' and 'southwest' from 2004 to 2019.

```{r, chunk9, echo=TRUE}
# subsetting of the tree circumference at the start and end of the study at 'northeast site'
ne<-subset(y, Site == "northeast")
# checking the first six lines of the data frame with head()command
head(ne)
# checking the structure of the data with str()command
str(ne)
# calculating the mean of tree circumference of 'northeast site' from 2004 to 2019
mean(ne$Circumf_2004_cm)
mean(ne$Circumf_2019_cm)
# calculating standard deviation of tree circumference of 'northeast site' from 2004 to 2019
sd(ne$Circumf_2004_cm)
sd(ne$Circumf_2019_cm)

# subsetting of the tree circumference at the start and end of the study at 'southwest site'
sw<-subset(y, Site == "southwest")
# checking the first six lines of the data frame with head()command
head(sw)
# checking the structure of the data with str()command
str(sw)
# the mean of tree circumference of 'southwest site' from 2004 to 2019
mean(sw$Circumf_2004_cm)
mean(sw$Circumf_2019_cm)
# the standard deviation of tree circumference of 'southwest site' from 2004 to 2019
sd(sw$Circumf_2004_cm)
sd(sw$Circumf_2019_cm)
```
## Question 8.  Creating a box plot of tree circumference at the start and end of the study at both sites
In this part of the assessment task, we are creating a box plot of tree circumference of northeast and southwest sites from 2004 to 2019 by using boxplot() command. 

```{r, chunk10, echo=TRUE}
# creating a boxplot of tree circumference of northeast and southwest sites from 2004 to 2019
boxplot(ne$Circumf_2004_cm, ne$Circumf_2019_cm, sw$Circumf_2004_cm, sw$Circumf_2019_cm, names = c("ne2004", "ne2019", "sw2004", "sw2019"), ylab="circumference (m)", las=2, main= "Tree growth at two plantation sites")
```
## Question 9. Calculate the mean growth over the past 10 years at each site.  
here we are subtracting the tree circumferences from year 2019 to 2004 of both northeast and southwest sites.
```{r, chunk11, echo=TRUE}
# calculating the growth difference by using subtraction command 
ne$growth <-ne$Circumf_2019 - ne$Circumf_2004_cm
head(ne)
sw$growth <-sw$Circumf_2019 - sw$Circumf_2004_cm
head(sw)
```
## Question 10. Use of the t.test and wilcox.test functions to estimate the p-value that the 10 year growth is different at the two sites.   
In this section, we are applying the the t.test and wilcox.test functions to estimate the p-value.
```{r, chunk12, echo=TRUE}
# using t.test
t.test(sw$growth, ne$growth)
# using wilcox.test
wilcox.test(sw$growth, ne$growth)
```







